Highlighting Disputed Claims on the Web

### 2009-10-30 papers/www_disputefinder/disputefinder.tex
Changes suggested by Tad

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/highlight_abortion.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_abortion_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.

@@

Dispute Finder consists of a server-side database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

In this paper, we describe the design of Dispute Finder, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/snippet_claim_article_fancy3.png}
	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

Dispute Finder has been influenced by previous work in many different fields, including sensemaking, web annotation, natural language processing, and information extraction. We discuss this work throughout the paper.

\subsection{Challenges}

During the design and implementation of Dispute Finder, we had to come up with solutions for several challenges:

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible. If the database's coverage is too small then users will rarely see snippets highlighted. If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying. We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.

\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted? There is a tradeoff between precision and recall. If we highlight a snippet that is not making a disputed claim then the user will be annoyed, but if we do not highlight a snippet that is making a disputed claim then Dispute Finding missed an opportunity to be useful. We currently run a textual entailment algorithm inside the browser extension that looks for phrases that look similar to a known disputed claim.

\item[How do we highlight snippets?] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed. Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt. We currently use a browser extension that checks for disputed claims on every page the user browses, and offer an API that other web sites can use to mark disputed claims on content that they serve.

\item[How should we explain a disputed claim?] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim. We currently use a simple list of articles arguing for and against the claim.

\item[What do people want?] To be useful for users, Dispute Finder needs to serve a real need that users have. We used interviews, user studies, and a small survey to try to learn what users want and what users are likely to use.
\end{description}

In the rest of this paper, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.

@@

If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use. We designed Dispute Finder is designed to cater to two personas. Each persona was created from interviews we conducted with people who we believe fit into these categories.

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that don't affect them (e.g. entertainment).

\todo{Move our personals to a ``people'' section}

\todo{Use interviews to get some actual observations here. These are just fillers.}

@@

\section{Related Work}

@@

Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate a {\it page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

@@

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.

@@

Dispute Finder can also be seen as an example of a tagging tool~\cite{Marlow2006,Golder2006}. Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags. In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.

\section{Trusting Online Content}

If a web user trusted all the content that they read, or were unconcerned that information they read might be wrong, then it is unlikely that they they would be much demand for a service such as Dispute Finder. Fortunately, there is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of registered Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.

This result was backed up by our interviews. Several participants told us that they regularly get information from sources that they don't entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.

There is also evidence that a significant group of people are interested in checking information they read on the web. Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web. Snopes.com contains information about urban myths such as ``eskimos have many words for snow''. Factcheck.org and Politifact.com investigate claims about US politics. According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand. Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts. In our survey, 64\% of respondents said that they often check information they read on a trusted site and 74\% of respondents said that they often check information they read by searching for other web pages with information about that topic.

@@

\section{What is Disputed?}
\label{sec:disputed}

@@

Currently most of our claims are automatically mined from Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

@@

\section{Finding Snippets}

@@

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=7cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

@@

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Baysian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Bulk page marking trades off some precesion for better coverage. When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them. Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.

@@

Detecting entailment between texts is a semantic analyss problem. Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

\section{Explaining Disputed Claims}

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selectinguse as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\section{Trustworthy Sources}

@@

Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliablity of a source based on how well it fits with what they already believe to be true.  As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

\section{Highlighting Snippets}

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user isn't interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it isn't making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

\section{Learning from Users}

We performed three qualitative ``think aloud'' user studies. The aim of these studies was to inform the iterative design of the Dispute Finder tool. The studies were not intended to validate the design of Dispute Finder as being correct.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}

@@

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realized that one could click on a disputed claim to bring up more information. Several users complained about Dispute Finder highlighting snippets that weren't making the claim Dispute Finder indicated.

@@

@@

@@

@@

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them or that they were expected to be knowledgeable about, but were less interested about applying it to pages about other topics, that they were less interested in. For topics that didn't affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''.

Most users were frustrated by the relatively poor accuracy and recall that Dispute Finder has at present. Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder didn't highlight anything. Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated. If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.

>>>>

In recent years, we have seen the emergence of a new class of applications that help users recognize and make sense of online dispute. In this paper, we describe Dispute Finder, an application that alerts a user when information they read online is disputed by a source that they might trust.

%The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time searching for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/highlight_abortion.png}
	\caption{Dispute Finder highlights text snippets that make disputed claims.}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7cm]{pictures/popup_abortion_shadow.png}
	\caption{Click on a highlighted snippet to see a popup interface with articles arguing for and against the claim.}
	\label{claimview}
	\end{center}
\end{figure}
\todo{Popup interface should contain a ``don't mark this'' button}

@@

%In this paper we describe Dispute Finder, a tool that alerts a user when information they read online is disputed by a source that they might trust. Our hope is that Dispute Finder will make it easier for a user to gain a broad view of a topic that they are interested in by exposing them to different points of view.

@@

Dispute Finder consists of a server-side database and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web. For each claim, the database contains references to articles on the web that support or oppose it, and hints about how to recognize that disputed claim on the web (Figure~\ref{snippet_claim_article}). The browser extension maintains its own local copy of the database, and runs a textual entailment algorithm on every sentence the user views to determine whether it is likely to be making a known disputed claim.

\todo{Should we mention the API? Cut from this version as tangential}

In this paper, we describe the design of Dispute Finder, the constituent problems that must be solved to make a tool like Dispute Finder work well, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{pictures/snippet_claim_article_fancy3.png}
	\caption{Snippets entail claims. Claims are entailed or contradicted by articles.}
	\label{snippet_claim_article}
	\end{center}
\end{figure}

@@

If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use. We used interviews to construct two personas, which model the two ways that we expect a user to use Dispute Finder.

{\it Skeptical Readers} want to know when something they read is disputed by a source that they might trust. They are skeptical about the accuracy of the information that they read and often check multiple sources to get different opinions on a topic. A user may behave like a skeptical reader for some topics and not others. For example a user may be skeptical when reading about topics that affect them (e.g. health, things important to their job, or things they are expected to be knowledgeable about), but disengaged when reading about topics that do not affect them (e.g. entertainment).

@@

\section{Background and Related Work}

There is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust. This has lead to a growing set of tools that aim to help users deal with disputed and biased information.

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of Democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Similarly, 51\% of Democrats regularly watch CNN, and yet only 35\% believe all or most of what CNN says. While these figures covered TV, rather than the web, Pew report that 48\% of web users people regularly follow search links to unfamiliar sources, and that users view online sources such as blogs with more skepticism that their print, broadcast, and cable counterparts.

These findings were backed up by our interviews. Several participants told us that they regularly get information from sources that they do not entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search. For example they might read Michael Moore because he is entertaining, or read articles mailed to them by friends.

\todo{Talk about people reading from a wide range of sources.}

There is also evidence that a significant group of people are interested in checking information they read on the web. Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web. Snopes.com contains information about urban myths such as ``eskimos have many words for snow''. Factcheck.org and Politifact.com investigate claims about US politics. According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand. Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts and so the real number of users who regularly check facts online is likely to be much higher.

To check our assumptions, we circulated a survey among members of a local debate club, who we anticipated would be a good match for our Skeptical Reader and Activist personals. Of the 23 people who responded, 91\% said that they sometimes or often check information they read on a trusted site (64\% often, 27\% sometimes) and 91\% said that they sometimes of often check information by searching for other web pages about the same topic (74\% often, 17\% sometimes).

\todo{Talk about our survey}

@@

Another key difference between prior annotation tools and Dispute Finder is that prior annotation tools allow a user to annotate {\it text on a page} while Dispute Finder attempts to allow a user to annotate a {\it claim} everywhere it appears on the web. If a user of an annotation tool adds an annotation to a page then their annotation will only appear on that page. If a user of Dispute Finder tells Dispute Finder to highlight a disputed claim, that claim will be highlighted on every web page on which Dispute Finder's algorithms determine that the claim appears. The closest annotation system to Dispute Finder is perhaps SparTag.us~\cite{Hong2009}, which uses an SHA hash to attach an annotation to an exact paragraph, irrespective of where it appears on the web; however a claim may be written in many different ways, and be part of many different paragraphs.

@@

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. These tools have a similar aim to Dispute Finder, but are limited to Wikipedia.

@@

Dispute Finder also has some similarity to tagging tools~\cite{Marlow2006,Golder2006}. Tagging tools allow users to collectively categorize information by associating it with a user-created set of tags. In the case of Dispute Finder, the tags are disputed claims, and the tagged entities are sentences that make those claims.

@@

\section{Design}

Creating a tool to manage disputed information requires designers to address a number of challenges, including:

\begin{description}
\item[Developing a corpus of disputed claims:] To be useful, the set of known disputed claims needs to be both large and credible. If the database's coverage is too small then users will rarely see snippets highlighted. If the database is not credible then users will often see snippets highlighted for which there is no credible evidence for other points of view.

\item[Detecting these disputed claims on the web:] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted? There is a trade-off between precision and recall. We do not want to highlight a snippet that is not making a disputed claim, but we do want to maximize the likelihood that we highlight a snippet that is making a disputed claim.

\item[Highlighting disputed claims for users:] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed. Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt. We also want to avoid distracting the user unnecessarily, while also making sure that they do notice disputed claims that they would care about.

\item[Providing tools that help users interpret disputed claims:] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim. We want to help a user understand both {\it who} holds other points of view and {\it why} other people hold different points of view.

\item[Determining Trustworthy Sources:] What sources should we consider ``trustworthy'' in the sense that they opinions are worth presenting to the user, and we should inform the user when a trustworthy source disagrees with what they are reading. There is a trade-off between showing a user sources that they will trust, and showing them sources that will expose them to a new point of view.

\end{description}

These challenges are not unique to dispute finder. They apply to any tool that informs a user about disputed information and helps users interpret this disputed information.

In the rest of this section, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.

\subsection{Developing a Corpus}
\label{sec:disputed}

@@

Currently most of our claims are automatically mined from Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American politicians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

@@

\subsection{Detecting Disputed Claims}

@@

\begin{figure}[t]
	\begin{center}
	\includegraphics[width=8cm]{pictures/nlp_client_server2.png}
	\caption{Client-side entailment: the entailment algorithm runs on the client, using a claim database downloaded from the server.}
	\label{nlp_client_server}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/paraphrases.png}
	\caption{Users can enter paraphrases of a claim to help the entailment algorithm.}
	\label{paraphrases}
	\end{center}
\end{figure}

@@

\item[Server-side classification:] The server uses the examples from the bulk page marking interface to train a classifier. We used a simple Bayesian classifier with n-grams as features. This classifier looks at the positive and negative examples given by the user and learns n-grams that should or should not be present in a snippet in order for it to make the claim.  Once the classifier has been trained, the server uses it to refine which of the rest of the results from Yahoo BOSS should be marked (Figure~\ref{training}).

@@

Bulk page marking trades off some precision for better coverage. When a user searches for a phrase, they can quickly find hundreds of snippets and mark them by clicking on them. Since they are reading the snippet out of context, they are more likely to mark a phrase incorrectly.

@@

Detecting entailment between texts is a semantic analysis problem. Our client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, inferring inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using Bayesian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

\subsection{Highlighting Disputed Claims}

The highlights show a user {\it which phrases} Dispute Finder believes are making disputed claims. This allows a user to ignore disputed claims that are made by text that the user is not interested in - such as user comments. The highlights also allow a user to see when Dispute Finder has incorrectly inferred that a phrase as making a disputed claims that it is not making. In such cases, the user is encouraged to help Dispute Finder improve its marking by clicking on the disputed claim and clicking on the ``report incorrect highlighting'' button from the popup interface.

\subsection{Helping Users Interpret Claims}

@@

\item[Article lists:] Dispute Finder shows the user two lists of articles, one of which contains articles arguing in favor of the claim, and the other of which contains articles arguing against the claim (Figure~\ref{article_list}). For each article, the interface shows a summary sentence that captures the core argument used by the article. A user can add any web page as a supporting article by browsing to the page, selecting ``use as evidence'' from a context menu (Figure~\ref{add_article}) and then saying what claim it supports or opposes (Figure~\ref{article_choose}).
\end{description}

@@

\subsection{Determining Trustworthy Sources}

@@

Unfortunately, as Pew Research discovered~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust are often those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. Similarly, Manjou~\cite{Manjou2008} found that people tend to measure the reliability of a source based on how well it fits with what they already believe to be true.  As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

\section{Evaluation}

We gathered information from users using user-studies, a survey, and a set of interviews. We performed three qualitative ``think aloud'' user studies. The aim of these studies was to inform the iterative design of the Dispute Finder tool. The studies were not intended to validate the design of Dispute Finder as being correct. We also interviewed most of our user study participants, and five additional people.

We found that most people were interested in having a tool like Dispute Finder, and were able to use Dispute Finder effectively as a Skeptical Reader. However we found that users were frustrated by the relatively low fraction of disputed claims that Dispute Finder currently highlights, and had some difficulty adding new claims themselves.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{pictures/popup_graph_crop.png}
	\caption{Argumentation graph interface for a disputed claim}
	\label{popup_graph}
	\end{center}
\end{figure}

@@

When browsing a page that had disputed claims highlighted, most users correctly inferred that these were sentences they should be skeptical about, but some users thought that we were saying they were wrong, rather than merely disputed. Not all users realized that one could click on a disputed claim to bring up more information. Several users complained about Dispute Finder highlighting snippets that were not making the claim Dispute Finder indicated.

Most users were frustrated by the relatively poor precision and recall that Dispute Finder has at present. Several users browsed to a page that they knew contained disputed claims, and were disappointed when Dispute Finder did not highlight anything. Several users were also frustrated when Dispute Finder highlighted phrases that did not make the claim Dispute Finder indicated. If Dispute Finder is to be adopted widely then we will need to significantly improve precision and recall, by building a bigger database of disputed claims, and improving the accuracy of our textual entailment algorithm.

Most people we interviewed were interested in applying Dispute Finder to particular areas that affected them (e.g. health) or that they were expected to be knowledgeable about (e.g. something relating to their work), but were less interested in applying it to pages about topics that they were less interested in. For topics that did not affect them users felt that misinformation was ``not important enough to bother with'', or that they could ``afford to be misinformed''. Users read about some topics (e.g. celebrity gossip) ``for entertainment'' or ``to relax'' and so they were less interested in making sure they properly understood those topics.

@@

\subsubsection{Claims}

@@

\subsubsection{The Article List}

@@

\subsubsection{The Argumentation Graph}

@@
